---
title: "Exercise 1"
format: html
editor: visual
---

## Import of necessary packages

The *tidyverse* package is imported to use `ggplot2`:

```{r, message=FALSE}
library(tidyverse)
```

## Sample generation

100 values are sampled from a log-normal-distribution:

```{r}
set.seed(42)
sample <- rlnorm(100, meanlog = 5, sdlog = 0.5)
```

The mean value of the sample is `r mean(sample)` and the standard deviation is `r sd(sample)`.

## Plots

The distribution of the data can be explored using different types of plots, e.g. histograms or violin plots.

The data is plotted first in a histogram with linear scales:

```{r}
ggplot(data = data.frame(sample), aes(x = sample)) +
  geom_histogram(binwidth = 15,
                 fill = "blue",
                 color = "white") +
  labs(title = "Histogram of log-normal-distribution (linear scale)", 
       x = "Value", 
       y = "Count")
```

Afterwards, the data is plotted in a histogram with log scales:

```{r}
ggplot(data = data.frame(log(sample)), aes(x = log(sample))) +
  geom_histogram(binwidth = 0.1,
                 fill = "blue",
                 color = "white") +
  labs(title = "Histogram of log-normal-distribution histogram (log scale)", 
       x = "log(Value)", 
       y = "Count")
```

Finally, the data is plotted in a violin plot:

```{r}
ggplot(data = data.frame(sample), aes(x = "", y = sample)) +
  geom_violin(fill = "blue", color = "black", alpha = 0.5) +
  labs(title = "Log-normal-distribution violin plot", 
       x = "1", 
       y = "Value")
```
